\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-09-30 gwnnDraft02.tex
edits

In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$. 

@@

Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles. $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.

@@

Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT. In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$. As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $. The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837},

@@

\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2

@@

The GW results of these cases are presented in figure~(\ref{fig:Haa}). In all cases, the summed GW signal is detectable by one or more proposed interferometers. When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors. As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.  This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum. The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature). Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable. 

@@

\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)}

@@

\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)}

@@

Where $T$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$. LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
GW signals produced from an early cosmological phase transition would be seen as a stocastic background. Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}. the PSI curves are constructed using information from the power law form of the signal,

@@

h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}

>>>>

In essence, this is a linear combination of the individual spectral shapes weighted by a power of their efficiency factors $\kappa^q$. 

@@

Where we have assumed an optimistic bubble wall velocity of $v \sim 1$ for runaway bubbles. $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{Huber_2008} of bubble wall collisions.

@@

Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT. In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$. As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $. The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{Breitbach:2018ddu,PhysRevD.49.2837}, given by:

@@

\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2,

@@

The GW results of these cases are presented in figure~(\ref{fig:Haa}). In all cases, the summed GW signal is detectable by one or more proposed interferometers. When relaxing the assumptions on $\beta/H$, the scenarios in figure~(\ref{fig:Haa}) are still detectable for values ranging between $\mathcal{O}(1)$ and $\mathcal{O}(100)$ The frequency dependence in Eq.~(\ref{eqn::spectralshape}) takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors. As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.  This is seen in figure~(\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum. The broadening can be substantial if the hidden sectors transition between a large gap of time. Assuming that the amplitudes of individual contributions are comparable, a temperature gap limit exists at which two or more individual peaks could be resolved.

@@

\rho^2 =  T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\;\;\; \textrm{(auto-correlated)},

@@

\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2 \;\;\;\: \textrm{(cross-correlated)},

@@

where $T$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$. LISA~\citep{Audley:2017drz} and B-DEICIGO~\citep{10.1093/ptep/pty078} are proposed to be single detector interferometers, where as BBO~\citep{PhysRevD.72.083005} and DEICIGO~\citep{Sato_2017} would be built from an array of multiple interferometers.
GW signals produced from an early cosmological phase transition would be seen as a stocastic background. Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{PhysRevD.88.124032}. The PSI curves are constructed using information from the power law form of the signal,

@@

h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta},
